Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-25 concurrency/CONCUR 2023/paper.tex
a few more edits and todos

\subsection{Templates vs. Internal Reorganization}
Our original goal was to verify an existing concurrent BST implementation with the template approach, refactoring as necessary but otherwise leaving the code unchanged. However, there is a fundamental mismatch between the template approach and the standard approach to deletion in a BST. The operations we have seen thus far can be factored into a data-structure-agnostic concurrent step (\lstinline{traverse}) and a concurrency-unaware data structure step (\lstinline{insert_op} or \lstinline{lookup_op}). When removing a node from a BST, on the other hand, we usually restructure the tree with a \lstinline{pushdown} operation, %include figure?
rotating three-node sections of the tree until the node to be deleted is at a leaf. This operation is simultaneously concurrency-aware (we must lock the nodes involved to avoid race conditions) and data-structure-specific (we need to know precisely which nodes to target and how to rearrange them). In fact, most of the existing template proofs either do not include deletion at all, or do a very lightweight form of deletion in which nodes are marked as ``deleted'' but are never actually removed from the data structure.

>>>>

\subsection{Templates vs. Internal Reorganization}
Our original goal was to verify an existing concurrent BST implementation with the template approach, refactoring as necessary but otherwise leaving the code unchanged. However, there is a fundamental mismatch between the template approach and the standard approach to deletion in a BST. The operations we have seen thus far can be factored into a data-structure-agnostic concurrent step (\lstinline{traverse}) and a concurrency-unaware data structure step (\lstinline{insert_op} or \lstinline{lookup_op}). When removing a node from a BST, on the other hand, we usually restructure the tree with a \lstinline{pushdown} operation, %include figure?
rotating three-node sections of the tree until the node to be deleted is at a leaf. This operation is simultaneously concurrency-aware (we must lock the nodes involved to avoid race conditions) and data-structure-specific (we need to know precisely which nodes to target and how to rearrange them). This contrasts with linked-list deletion, which only involves the target node and its immediate neighbors. In practice, the existing template proofs for tree structures either do not include deletion at all, or use a very lightweight form of deletion in which nodes are marked as ``deleted'' but are never actually removed from the data structure.
